---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

###read raw data after fork in github and git clone in Git bash
```{r}
RData <- unzip("C:/Users/Kati/RepData_PeerAssessment1/activity.zip")
RData<- read.csv("./activity.csv", header=TRUE)
```
## What is mean total number of steps taken per day?
1 Summarize steps by day and store in Sdate   
2 Create a histogram of the  sum steps per day   
3 Calculate the mean and the median of the total number of steps per day   
```{r}
Sdata<-aggregate(steps~date, data=RData, FUN="sum")
hist(Sdata$steps)
mean(Sdata$steps)
median(Sdata$steps)
```
## What is the average daily activity pattern?
1 Create data set for eveluating average daly activity pattern  
2 Plot the average daly activity pattern by creating time series plot  
3 Find the that 5-minutes interval which has a maximum number of steps on average acrass all days
```{r}
SDMData<-aggregate(steps~interval, data=RData,FUN="mean")
plot.ts(SDMData$steps, main="average daly activity pattern", ylab="average stpes", xlab="5 minute interval")
which.max(SDMData$steps)
```
## Imputing missing values
1 Calculate  the total number of missing values in the dataset  
2 Fill missing value with corresponding intervals mean value  
3 Summarize steps by day and store in SNdate for the filled data set  
4 Create a histogram of the  sum steps per day  
5 Calculate the mean and the median of the total number of steps per day  
```{r}
sum(is.na(RData[1]))
library(dplyr)
NData<-RData
sapply(unique(RData$interval), function(x)
  NData[!complete.cases(NData)&(NData$interval==x),1]<<-SDMData$steps[SDMData$interval==x])
SNdata<-aggregate(steps~date, data=NData, FUN="sum")
hist(SNdata$steps)
mean(SNdata$steps)
median(SNdata$steps)
```


## Are there differences in activity patterns between weekdays and weekends?

1 Create a new factor variable in the dataset with two levels – “weekday”
and “weekend” indicating whether a given date is a weekday or weekend
day.  
2 Make a panel plot containing a time series plot (i.e. type = "l") of the
5-minute interval (x-axis) and the average number of steps taken, averaged
across all weekday days or weekend days (y-axis).  
```{r}
NData$date<-as.Date(NData$date,"%Y-%m-%d")
NData$weektime <- as.factor(ifelse(weekdays(NData$date) %in% 
                c("vasárnap","szombat"),"weekend", "weekday"))
SDMNData<-aggregate(steps~interval+weektime, data=NData,FUN="mean")
library("lattice")
p <- xyplot(steps ~ interval | factor(weektime), data=SDMNData, 
       type = 'l',
       main="Average Number of Steps Taken 
       \nAveraged Across All Weekday Days or Weekend Days",
       xlab="5-Minute Interval (military time)",
       ylab="Average Number of Steps Taken")
print (p) 
```
